---
title: "2016/2017/2018 - OddDataAnalysis"
author: "Mercan Karacabey"
date: "19 11 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Used This Libraries
```{r, warning=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)
```

```{r, warning=FALSE}
dat <- readRDS("car_data_aggregate.rds")
```


head and tail of excel data

```{r}
head(dat)
tail(dat)
```

## Time to make some analysis

Firstly, we should learn brand names.
```{r,warning=FALSE}
dat %>% 
  select(brand_name) 
```

-----------------------------------------------------------------------------------------

On the below, automobiles which sold more than others in 2016,2017,2018.

```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% 
  arrange(desc(auto_total)) %>% filter(brand_name != 'TOPLAM:')
```

```{r, warning=FALSE}
result1 <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% 
  arrange(desc(auto_total)) %>% filter(brand_name != 'TOPLAM:')
```

```{r , echo=FALSE}
ggplot(result1,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __ALFA ROMEO__

Most automobile sales for Alfa Romeo.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% arrange(desc(auto_total))
```
For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ALFA ROMEO') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```


## Analysis for __ASTON MARTIN__

```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'ASTON MARTİN') %>% arrange(desc(auto_total))
```
Only, was done sale in 2016-Jan for Aston Martin. 

## Analysis for __AUDI__

Most automobile sales for Audi.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'AUDI') %>% arrange(desc(auto_total))
```
For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'AUDI') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```
```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'AUDI') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```
For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'AUDI') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'AUDI') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __BENTLEY__

Most automobile sales for BENTLEY.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% arrange(desc(auto_total))
```
For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```
```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BENTLEY') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __BMW__

Most automobile sales for BMW.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'BMW') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```


## Analysis for __CHERY__

Most automobile sales for CHERY.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CHERY') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __CITROEN__

Most automobile sales for CITROEN.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'CITROEN') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```


## Analysis for __DACIA__

Most automobile sales for DACIA.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DACIA') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __DS__

Most automobile sales for DS.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'DS') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __FERRARI__

Most automobile sales for FERRARI.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FERRARI') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```
## Analysis for __FIAT__

Most automobile sales for FIAT.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'FIAT') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __RENAULT__

Most automobile sales for RENAULT.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'RENAULT') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

## Analysis for __VOLKSWAGEN__

Most automobile sales for VOLKSWAGEN.
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% arrange(desc(auto_total))
```

For 2018,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2018) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2017,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2017) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```

For 2016,
```{r, warning=FALSE}
dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r, warning=FALSE}
tabl <- dat %>% 
  select(brand_name,auto_total,auto_dom,comm_dom,total_imp,total_dom,year,month) %>% filter(brand_name == 'VOLKSWAGEN') %>% filter(year==2016) %>% mutate(meanOfAutoTotal = mean(auto_total))  %>% arrange(desc(auto_total))
```

```{r , echo=FALSE}
ggplot(tabl,aes(x=month,y=auto_total))+geom_point()
```
